Titeln på avhandlingens språk

### 2023-03-13 body/part1/chapter2-relatedwork/relatedwork.tex
ncs research

@@

\subsection{Emulation of \glsfmtshortpl{NCS}}

>>>>

\todo[inline]{Maybe expand to evaluating performance of XR? Prototyping of XR?}

@@

\textcite{chetoui2022arbench}: ARBench, a benchmarking suite for AR.
Corresponds to a software package including a multitude of AR workloads, emulating the load placed on the the hardware.
Only considers locally-running AR, not network.
Does not emulate human behavior, uses traces of AR applications.

\textcite{george2020openrtist}: OpenRTiST, benchmarking workload for Edge Computing, AR
Based on stable diffusion.

\subsection{Experimental research in \glsfmtshortpl{NCS}}

A significant amount of work has been dedicated to the modeling and performance characterization of \glspl{NCS} due to their potential benefits for industrial and commercial settings~\cite{lu2016real,hespanha2007survey,zhang2013network,zhang2016survey}.
Most of the large literature concerning \glspl{NCS}, however, follows a theoretical approach, with only small fraction of it dealing with experimental studies.
\gls{NCS} studies are complex due to the inter-domain nature of these systems, requiring expertise in the fields of communication networks, computing, and control theory.

Within the body of works relating to experimental research on \glspl{NCS}, we identify three distinct approaches: fully practical, fully simulated, and emulated approaches that combine components of the first two.

In a fully practical approach, the experimental setup uses real systems and hardware to test and validate the performance of the \gls{NCS}.
This approach is straightforward to implement, and can be very useful for evaluating the real-world applicability of the system, but can be costly and time-consuming.
Examples of the application of this approach can be found in studies such as~\cite{drew2005networked,baumann2018evaluating,li2014wireless,cuenca2019periodic}.
These studies implemented wireless and microcontroller-based systems for control and validated them on a physical prototype.

In~\cite{drew2005networked}, the authors present a \gls{NCS} model which considers both random packet delay and loss on both the sensor and actuator sides of the feedback loop.
They validate their design on a physical testbed consisting of inverted pendula controlled from a central computation point over Wi-Fi.
A similar testbed is employed for validation in~\cite{baumann2018evaluating}, in which the authors develop an evaluation methodology for wireless \gls{NCS}.\@
\cite{li2014wireless} implements a wireless microcontroller-based system for vibration control and validates it on a physical prototype comprising a cantilever beam controlled using an \acs{IEEE} 802.15.4 \gls{WPAN} system.\@ \cite{cuenca2019periodic} discusses the design and implementation of a periodic event-triggered sampling and dual-rate control techniques for wireless control, and validate their contributions on a four-rotor autonomous drone platform controlled over WiFi.
\emph{NCSbench}~\cite{zoppi2020ncsbench}, an open-source \gls{NCS} benchmarking platform designed with reproducibility in mind built using the \citetitle{LEGOMindstormsEV3}~\cite{LEGOMindstormsEV3} platform, is another such example.

Completely simulated setups, on the other hand, rely on computer simulations to evaluate the \gls{NCS}'s performance.
This approach is less expensive and faster than the practical approach but may not fully capture the real-world complexities of the system.
Examples of tools and frameworks for the implementation of this approach can be found in works such as~\cite{andersson2005simulation,eyisi2012ncswt}.

A simulated approach is employed in~\cite{du2009novel}, in which the authors develop a novel \emph{Smith} predictor to compensate for varying latencies in wireless \glspl{NCS} and validate it using the \emph{TrueTime}~\cite{henriksson2002truetime} simulator.
In~\cite{chen2015synchronous} the authors validate and evaluate a number of synchronous control strategies for three-motor setups using completely simulated \glspl{NCS} environments.\@
\cite{wu2012application} introduces the concept of \emph{network predictive control} in and uses it to balance a simulated inverted pendulum over a simulated wireless network.\@
\cite{ma2019optimal} proposes an optimal dynamic scheduling strategy that optimizes performance of multi-loop control systems and validate it by simulating a four-loop control system over an \acs{IEEE} 802.15.4 \gls{WPAN}.

Finally, network and hardware-in-the-loop approaches, which aim to strike a balance between realism and efficiency, have also been employed in literature.
Network-in-the-loop refers to experimental setups in which the \emph{network} is instead simulated or emulated.
Such approaches have, for instance, been used to study the effects of the \gls{CSMA/CD} medium access control mechanism on plant stability, as in~\cite{natale2004inverted}.
Hardware-in-the-loop approaches, referring to \gls{NCS} setups in which a real network interacts with a simulated or emulated control system, are particularly prevalent in the field of \emph{smart grid} control.
An example of the application of such an approach can be found in~\cite{wang2020inverter}, in which the authors introduce and validate a novel three-level coordinated control method for photovoltaic inverters.
